%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Rohit Muthukumarasamy}}}} % First name
	
	\vspace{6pt}
	
	{\Large Software Developer $\sim$ Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text 
    \icon{Phone}{11}{+91-8838039162}\\
    \icon{MapMarker}{11}{Chennai, India}\\
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\icon{Envelope}{11}{\href{mailto:rohitmuthukumarasamy@gmail.com}{rohitmuthukumarasamy@gmail.com}}\\	
    \icon{Github}{11}{\href{https://github.com/ropkg}{Rohit Muthukumarasamy}}\\
    \icon{LinkedinSquare}{11}{\href{www.linkedin.com/in/rohit-muthukumarasamy-a5b2102aa/}{Rohit Muthukumarasamy}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    %Dummy text
	A recent graduate skilled in problem-solving, collaboration, and emerging technologies. Proficient in developing robust Python solutions for complex projects, particularly focusing on data analysis and visualization. Successfully achieved a 40\% reduction in runtime through optimized data processing methods, significantly enhancing project efficiency. \\
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Python , Java , C++ , C , SQL , HTML , CSS , Javascript.  
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Tableau, Power-BI, MS-Excel, AWS, Firebase, GCP, Spark, GIT, Tensorflow, PyTorch, NumPy, Atlassian JIRA.
    \end{minipage}
    
    
\end{minipage}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{10/2021 - 5/2023}
		{M.Tech Computer Science and Technology}
		{Post-Graduate}
		{SRM Institute of Science and Technology, Chennai}
	
\end{entrylist}
%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{Python}
		{Emotion Recognition using Accoustic Features}
		{{\href{https://github.com/ropkg/}{\icon{Github}{11}}}}
		{%Dummy text 
        Achieved 78\% accuracy in identifying human emotions by utilizing the Librosa library to extract distinctive voice features.}
	\entry
		{Python}
		{Pandemic Outbreak prediction using Time-Series Analysis}
		{{\href{https://github.com/ropkg/COVID-19-Prediction-using-Time-Series-Analysis/tree/main}{\icon{Github}{11}}}}
		{%Dummy text 
        Engineered a sophisticated COVID-19 prediction model with an 80\% accuracy rate, employing advanced Time Series analysis and Machine Learning techniques in Python. Executed precise forecasting of virus spread, furnishing insightful data for strategic decision-making..}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {5/2023 -- 12/2023}
		{Intern - Drone Pilot}
		{Chandigarh Institute of Drones}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Developed Unmanned Aerial Vehicles (UAVs) and Quadcopter Drones as part of a comprehensive project. Implemented a machine learning model for human identification, enhancing disaster management capabilities through analysis, design, development, testing, and support.
            \item Developed and implemented advanced RADAR systems, state-of-the-art autopilot systems, and highly efficient payload delivery mechanisms for deployment across a diverse range of military applications. This multifaceted project involved the integration of cutting-edge technologies to enhance operational capabilities and address various military requirements.
        \end{itemize} 
        \texttt{Python} \slashsep \texttt{IoT}}
	\entry
		{9/2022 -- 4/2023}
		{Tech Intern}
		{Bank of America}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Worked as a part of Reconciliation and Operational Client (ROCS) team Developed automation program which automated entries during Reconciliation process resulting in reduction of time taken by 25 \%.
            \item Facilitated and oversaw sprint and scrum meetings, served as a Scrum Master, and contributed to the management of business requirements within an Agile framework.
            \item Immersed in the intricacies of the banking domain, gaining in-depth understanding of diverse operations, security applications, and widely adopted enterprise solutions. Expanded knowledge base to include mutual funds, stocks, equity, investment banking, and taxation.
        \end{itemize} 
        \texttt{Python} \slashsep \texttt{SQL} \slashsep \texttt{MS-Excel}}
	\entry
		{5/2019 -- 6/2019 \\\footnotesize}
		{Intern}
		{BSNL Telecommunications}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Employed Packet Tracer software to construct intricate networking protocols, troubleshoot issues, and simulate their functionality within a controlled environment.
            \item Implemented encryption protocols and load-balancing algorithms for testing supercomputers in telecommunications, enhancing security and optimizing resource allocation.
        \end{itemize} 
        \texttt{Cisco Packet tracer} \slashsep \texttt{LINUX}}
\end{entrylist}
\vspace{-10 pt}
\cvsect{Certifications}
\begin{entrylist}
    \entry
		{2022}
		{Google Technical Support Fundamentals}
		{Coursera}
        {Google}
    \entry
		{2022}
		{Foundations of Business Intelligence}
		{Coursera}
        {Google}
\end{entrylist}
\end{document}
